Superphy: Real-time prediction of \textit{E. coli} phenotype using graph-based genome sequence storage and retrieval with the \textit{spfy} module

### 2017-12-07 paper-proposal.tex
STOP: not sure i want to focus too much on the subtyping in our proposal

% include a notification if this is an update from a previous publication in the Web Server issue, and in that case, include an estimate of the number of users and the number of citations.
% For web servers, or essentially similar web servers, that have been the subject of a previous publication, including publication in journals other than NAR, there is a minimum two-year interval before re-publication in the Web Server Issue.
Our proposal covers an update to Superphy \citep{whiteside2016superphy}, an online predictive genomics platform targeting \textit{E. coli}.
The update, called Spfy, demonstrates a novel approach to result storage and retrieval for computational workflows.
Many of the comparative analyses that are run on current computational workflows chain different analysis software, but lack storage methods which examine the relation between results.
% IF THE WEBSITE IMPLEMENTS A META-SERVER OR COMPUTATIONAL WORKFLOW, the summary MUST describe 1) significant added value beyond the simple chaining together of existing third party software or the calculation of a consensus prediction from third party predictors and classifiers; and at least one of the following: 2) how user time for data gathering and multi-step analysis is significantly reduced, or 3) how the website offers significantly enhanced display of the data and results.
Instead, we can store output from different software together, in the context of a genome graph and thus link analysis results with epidemiological data.
In Spfy, we demonstrate the use knowledge graphs and a persistant graph database to store results from a variety of subtyping modules for \textit{E. coli} and integrate external sample information.
This approach scales to the large number of WGS data being accumulated, and allows comparative analysis between different analysis software.

>>>>

% include a notification if this is an update from a previous publication in the Web Server issue, and in that case, include an estimate of the number of users and the number of citations.
% For web servers, or essentially similar web servers, that have been the subject of a previous publication, including publication in journals other than NAR, there is a minimum two-year interval before re-publication in the Web Server Issue.
Our proposal covers an update to Superphy \citep{whiteside2016superphy}, an online predictive genomics platform targeting \textit{E. coli}.
The update, called Spfy, uses graph datastructures to store and retrieve results for computational workflows.
We demonstrate how graph datastructures scale to the large number of WGS data being accumulated, and allows statistical significance testing between different analysis software.
To build these graphs, Spfy first provides real-time subtyping through a ReactJS-based website, where user-defined analyses options are selected. 
The chosen analyses are ran in parallel using task queues and Docker containerization, and the results immediately displayed to the user following their completion.
Subtyping options are O-antigen, H-antigen, Shiga-toxin 1 (Stx1), Shiga-toxin 2 (Stx2), and Intimin typing, VF and AMR annotation, and pan-genome generation.

Many of the comparative analyses that are run on current computational workflows chain different analysis software, but lack storage methods which examine the relation between results.
% IF THE WEBSITE IMPLEMENTS A META-SERVER OR COMPUTATIONAL WORKFLOW, the summary MUST describe 1) significant added value beyond the simple chaining together of existing third party software or the calculation of a consensus prediction from third party predictors and classifiers; and at least one of the following: 2) how user time for data gathering and multi-step analysis is significantly reduced, or 3) how the website offers significantly enhanced display of the data and results.
Instead, we can store output from different software together, in the context of a genome graph and thus link analysis results with epidemiological data.
In Spfy, we demonstrate the use knowledge graphs and a persistant graph database to store results from a variety of subtyping modules for \textit{E. coli} and integrate external sample information.
This approach

### 2017-12-07 paper-webserver.tex
STOP: not sure i want to focus too much on the subtyping in our proposal

i) The upload begins through the ReactJS-based website, where user-defined analyses options are selected. The results of these chosen analyses are immediately reported to the user following their completion, while the remaining analyses are subsequently completed and stored in the database without interaction from the user. The public web service accepts up to 200 MB of genome files (50 genomes uncompressed, or 120 genomes compressed) at a time, though an unlimited amount of data can be submitted locally.

>>>>

i) The upload begins through the ReactJS-based website, where user-defined analyses options are selected. The results of these chosen analyses are immediately dispalyed to the user following their completion, while the remaining analyses are subsequently completed and stored in the database without interaction from the user. The public web service accepts up to 200 MB of genome files (50 genomes uncompressed, or 120 genomes compressed) at a time, though an unlimited amount of data can be submitted locally.
